---
title: "emr-cluster package"

output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  error = T
)
options(tibble.print_min = 4L, tibble.print_max = 4L, knitr.kable.NA = '')
```

## Development version
```{r , warning=FALSE,message = FALSE}
# install.packages("remotes")
#remotes::install_github("DHLab-TSENG/emr_clust")
```

## Useage

The goal of TEST is to unsupervised machine learning analysis process integration (including feature selection, dimension reduction, group analysis, visualization of group results, etc.)

This is a basic example which shows you how to solve a common problem:

```{r example, echo=TRUE, warning=FALSE,message = FALSE}

library(TEST)
library(FactoMineR)
library(tidyverse)
library(reshape2)
library(data.table)
library(knitr)
## basic example code

#for categorical dataset with combine dimention reduction & clustering method example
data(tea)
# I. Data doing feature selection + dimention reduction + clustering with result presentation for distribution of variables
emr_cat<-emr_clust(tea[,1:13],
                   method =c("MCAk"),
                   kmoCutoff = 0.5,
                   nclus=c(4:5),
                   ndim=c(2:3),
                   group="Tea",
                   nstart=50)
#show the tuning output table
kable(head(emr_cat$clust_out$tune_table),"html")
#show the statistic table
kable(head(emr_cat$statistics_table$PC_data),"html")
kable(head(emr_cat$statistics_table$attr_data),"html")
kable(head(emr_cat$statistics_table$use_table),"html")
#Biplot of the first and second principal components
emr_cat$biplot$clustering_biplots
#Profile the number and proportion of case in each cluster
emr_cat$biplot$profile_by_cluster_integrated
#Profile the number and proportion of case in each group
emr_cat$biplot$profile_by_group_integrated
# II. Visualization
#  1. Wind_rose_plot
pic<-wind_rose_plot(clustering_output = emr_cat, plot_value = "Not" )
pic$overlapped
pic$seperated
#  2. Sensitivity + Specificity plot
sen_spe_out<-sen_spe(clustering_output = emr_cat)
sen_spe_out

#for numerical dataset with seperate dimention reduction & clustering method example
data(iris)

# I. Data feature selection + dimention reduction + clustering with result presentation for distribution of variables
emr_numeric<-emr_clust(iris,
                       method =c("PCA","Kmean"),
                       center = TRUE,
                       scale = TRUE,
                       kmoCutoff = 0.5,
                       nclus=c(4:5),
                       ndim=c(2:3),
                       group="Species",
                       attr.params=list( fill="blue", color="darkred"),
                       text.params=list(alpha = 0.9))

#show the tuning output table
kable(head(emr_numeric$clust_out$tune_table),"html")
#show the statistic table
kable(head(emr_numeric$statistics_table$PC_data),"html")
kable(head(emr_numeric$statistics_table$attr_data),"html")
kable(head(emr_numeric$statistics_table$use_table),"html")
#Biplot of the first and second principal components
emr_numeric$biplot$clustering_biplots
#Profile the number and proportion of case in each cluster
emr_numeric$biplot$profile_by_cluster_integrated
#Profile the number and proportion of case in each group
emr_numeric$biplot$profile_by_group_integrated


```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
